INFOMDA2: Group Assignment

### 2025-01-15 code/analysis.qmd
change to loocv

```{r}
set.seed(123)
model_benchmark <- train(class ~ ., data = data_benchmark, method = "glm", family = "binomial", trControl = trainControl(method = "cv", number = 10))

@@

data_7 <- data %>%
  select(sig_7, class) %>% 
  train(class ~ ., data = ., method = "glm", family = "binomial", trControl = trainControl(method = "cv", number = 10))

@@

```{r}
logit_scree <- data_pca %>%
  select(pc1, class) %>%
  train(
    class ~ .,
    data = .,
    method = "glm",
    family = "binomial",
    trControl = trainControl(method = "cv", number = 10)
  )

@@

```{r}
logit_greaterthan1 <- data_pca %>% 
  select(all_of(pc_greaterthan1), class) %>%
  train(
    class ~ .,
    data = .,
    method = "glm",
    family = "binomial",
    trControl = trainControl(method = "cv", number = 10)
  )

@@

summary(logit)
```

>>>>

```{r}
set.seed(123)
model_benchmark <- train(class ~ ., data = data_benchmark, method = "glm", family = "binomial", trControl = trainControl(method = "LOOCV"))

@@

data_7 <- data %>%
  select(sig_7, class) %>% 
  train(class ~ ., data = ., method = "glm", family = "binomial", trControl = trainControl(method = "LOOCV"))

@@

```{r}
logit_scree <- data_pca %>%
  select(pc1, class) %>%
  train(
    class ~ .,
    data = .,
    method = "glm",
    family = "binomial",
    trControl = trainControl(method = "LOOCV")
  )

@@

```{r}
logit_greaterthan1 <- data_pca %>% 
  select(all_of(pc_greaterthan1), class) %>%
  train(
    class ~ .,
    data = .,
    method = "glm",
    family = "binomial",
    trControl = trainControl(method = "LOOCV")
  )

@@
